A radiocarbon data based evaluation of Cultural Transmission in Bronze Age burial rites of Central, Northern and North-western Europe

### 2018-12-01 02_Materials_and_Methods.Rmd
and even more

1. Downloading the Radon-B dataset with the R package c14bazAAR [@schmidC14bazAARDownloadPrepare2018], which allows to access several open radiocarbon archives. (11048)
2. Removing all dates without age information or age information outside of the limits of the Intcal13 calibration curve: 71 - 46401 BP [@reimer_intcal13_2013]. (10956)
3. Calibrating the ^14^C dates with the R package Bchron [@haslettSimpleMonotoneProcess2008], which implements the calibration algorithm with numerical integration.
4. Reducing date selection to all dates whose $2\sigma$ calibrated age range overlap by at least one year with the predefined window of interest: 2200 -- 800 calBC. (7543)
5. Reducing the date selection to all dates taken from graves as indicated by the *Feature type* variable. (2361)
6. Transforming the variable *Feature type* via pattern matching to two new variables *burial type* (inhumation/cremation/unknown) and *burial construction* (mound/flat/unknown).
7. Manually defining a rectangular (EPSG:102013) research area with sufficient information in Central-, Northern and Northwesetern Europe based on perceived spatial date distribution (Figure XXX).
8. Reducing date selection to dates within the research area. (1894)
9.

- Main steps of data preparation and grouping

>>>>

1. Downloading the Radon-B dataset with the R package c14bazAAR [@schmidC14bazAARDownloadPrepare2018], which allows to access several open radiocarbon archives. (11048 dates)
2. Removing all dates without age information or age information outside of the limits of the Intcal13 calibration curve: 71 - 46401 BP [@reimer_intcal13_2013]. (10956 dates)
3. Calibrating the ^14^C dates with the R package Bchron [@haslettSimpleMonotoneProcess2008], which implements the calibration algorithm with numerical integration.
4. Reducing date selection to all dates whose $2\sigma$ calibrated age range overlap by at least one year with the predefined window of interest: 2200 -- 800 calBC. (7543 dates)
5. Reducing the date selection to all dates taken from graves as indicated by the *Feature type* variable. (2361)
6. Transforming the variable *Feature type* via pattern matching to two new variables *burial type* (inhumation/cremation/unknown) and *burial construction* (mound/flat/unknown).
7. Manually defining a rectangular (EPSG:102013) research area with sufficient information in Central-, Northern and Northwestern Europe based on perceived spatial date distribution (Figure **TODO**).
8. Reducing date selection to dates within the research area. (1894 dates)
9. Removing ^14^C date doubles with tools of c14bazAAR. (1848 dates)
10. Transforming data from the meaning *^14^C dates on graves* to *burial type at a certain time*. This is a more complex process, because **TODO** (1704 graves)
11. Defining macroregions. **TODO**
12. Reducing the date selection to the space covered by the macroregions and attributing the dates to the respective units. (1562 graves)

The resulting dataset **TODO**
